\documentclass[]{resume}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\begin{document}

% Personal info

\namesection{Carlos}{Lezama}{Data Engineer}
{\contactline
{\href{https://celj.github.io}{celj.github.io}}
{\href{https://www.github.com/celj}{celj}}
{\href{mailto:carloselezamaj@gmail.com}{carloselezamaj@gmail.com}}
{\href{tel:+525561337361}{+52 55 6133 7361}}
}

% Column 1

\begin{minipage}[t]{0.70\textwidth}

% Summary

\section{Summary}

Excited to apply 2+ years of experience in statistical modelling towards developing data-driven solutions for risk analysis and strategic management. Focused in leveraging cutting-edge technologies and tools to build scalable and reliable data infrastructures. Enabling accurate and timely decision-making through these processes is of utmost importance.

% Experience

\section{Relevant Experience}

\runsubsection{Data Engineer}
\descript{@ \, RappiCard}
\location{Feb 2023 - Present // Remote}
\vspace{\topsep}
\begin{tightemize}
\sectionsep
\sectionsep
\item Contributed to the successful migration of data from one Snowflake environment to another, resulting in cleaner and improved data workflows for all teams in Mexico.
\item Developed and maintained automated data validation and testing processes to ensure data accuracy and completeness post-migration.
\item Responsible for securely sharing hashed information with universities for research purposes, while ensuring compliance with all relevant privacy laws and regulations.
\item Worked collaboratively with cross-functional teams to define data requirements and ensure data quality and consistency.
\end{tightemize}
\sectionsep

\runsubsection{Teacher}
\descript{@ \, Datalab ITAM}
\location{Jan 2022 - Present // Mexico City}
\begin{tightemize}
\sectionsep
\item Designed and delivered engaging course materials for Machine Learning courses.
\item Provided personalized feedback and guidance to students to help them succeed on projects with a social focus.
\end{tightemize}
\sectionsep

\runsubsection{Customer Lifecycle Analyst}
\descript{@ \, RappiCard}
\location{May 2022 - Feb 2023 // Remote}
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\sectionsep
\item Developed statistical analyses to measure and increase the share and the engagement of our credit card in the market.
\item Estimated the preferences of our clients for different credit cards based on information granted by the credit bureau.
\item Collaborated in the planning of strategies for increasing credit lines to maximize profits based on the consumption and payment patterns of our customers.
\end{tightemize}
\sectionsep

\runsubsection{Web Developer}
\descript{@ \, Datalab ITAM}
\location{Jan 2022 - Dec 2022 // Remote}
\begin{tightemize}
\sectionsep
\item Developed and redesigned ITAM's data science laboratory website using Hugo and Netlify.
\item Worked closely with students from different disciplines in the development of an educational application powered by augmented reality.
\end{tightemize}
\sectionsep

\runsubsection{Analytics Intern}
\descript{@ \, DiDi Food}
\location{Dec 2021 - Apr 2022 // Remote}
\begin{tightemize}
\sectionsep
\item Evaluated revenue optimization strategies to increase penetration and capture market shares for Mexico, Central America, and Colombia.
\end{tightemize}
\sectionsep

\runsubsection{Blockchain Developer Trainee}
\descript{@ \, BlockchainDevs ITAM}
\location{Feb 2020 - Dec 2021 // Mexico City}
\begin{tightemize}
\sectionsep
\item Upskilled in the mathematical foundations of Blockchain and smart contract programming on the Ethereum network using Solidity.
\end{tightemize}
\sectionsep

% Column 2

\end{minipage}
\hfill
\begin{minipage}[t]{0.25\textwidth}

% Education

\section{Education}
\subsection{Instituto Tecnológico \\ Autónomo de México (ITAM)}
\location{2018 - 2023 // Mexico City}
\sectionsep
Bachelor of Economics \\
Minor in Economic Theory \\
\sectionsep
\sectionsep

% Skills

\section{Skills}
\subsection{Programming Languages}
\sectionsep
JavaScript,
Python, \\
R,
Solidity,
SQL
\sectionsep
\sectionsep
\subsection{Libraries / Frameworks}
\sectionsep
Airflow,
Ethereum,
% Flutter,
Gatsby, \\
Hugo,
Kafka,
% Node.js,
Polars, \\
scikit-learn,
TensorFlow, \\
tidyverse,
tidymodels
\sectionsep
\sectionsep
\subsection{Tools / Platforms}
Anaconda,
AWS,
Databricks, \\
dbt,
Docker,
Git,
Google Cloud, \\
Kubernetes,
Microsoft Azure,
Netlify,
Snowflake
\sectionsep
\sectionsep
\subsection{Design}
Canva,
CSS/Sass,
LaTeX
\sectionsep
\sectionsep

% Courses

\section{Relevant Courses}
\subsection{Empirical Industrial \\ Organization}
\location{Fall 2022 // ITAM}
\sectionsep

\subsection{Advanced \\ Microeconometrics}
\location{Spring 2022 // ITAM}
\sectionsep

\subsection{Simulation Theory}
\location{Fall 2021 // ITAM}
\sectionsep

\subsection{Statistical Learning Theory}
\location{Spring 2021 // ITAM}
\sectionsep
\sectionsep

% Interests

\section{Interests}
Learning languages, \\
making music,
traveling, \\
writing poetry

\end{minipage}
\end{document}
